\documentclass{UCF_ETD}
% \usepackage{times} % obsolete font package
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage{datetime, fmtcount, etoolbox, fcprefix}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{cite}
\usepackage{graphics}
\usepackage{color,soul}
\usepackage{multirow,makecell}
% \usepackage[backend=biber,style=numeric]{biblatex}    
% %Use absolute paths to .bib-files for the subfiles to understand their location:
\usepackage{float}
\usepackage{chapterbib}
\usepackage{subfiles}
\newcommand{\ignore}[1]{}
\newcommand{\tss}[1]{\textsuperscript{#1}}
\renewcommand{\ul}{}
\newcommand{\tsu}[1]{\textsubscript{#1}}
\newcommand{\td}{\textasciitilde}



\title{\uppercase{Corticomuscular adaptation to mechanical perturbations in a seated locomotor task}} %Must be typed in all caps.
\author{\uppercase{Seyed Yahya Shirazi}} % typed in all caps



\prevdegreeii{B.Sc. AmirKabir University of Technology (Tehran Polytechnic), 2011}
\prevdegreei{M.Sc. AmirKabir University of Technology (Tehran Polytechnic), 2014}
% commands available for 
% \prevdegreei{ }
% \prevdegreeii{ }
% \prevdegreeiii{ }

\thesisname{dissertation}
% \thesisname prints out document type. Replace bracket text with dissertation for Ph.D students

\degreename{Doctor of Philosophy in Mechanical Engineering}
% type out degree name here.

\departmentsname{Mechanical and Aerospace Engineering}
% replace with department name if applicable.  Otherwise, do not include.

%\schoolname{Kenneth G. Dixon School of Accounting}
% replace with school name if applicable.  Otherwise, do not include.

\collegename{Engineering and Computer Science}
% replace with college name

\termname{Spring}
% replace with semester

\termyear{2021}
% replace with year. Term year is also used to generate copyright year.

\advisorname{Helen J. Huang}
% replace with Major Professor if applicable.  Otherwise, do not include.


\begin{document}

\frontmatter
% applies roman numerals as page numbers

\maketitle
% prints out school info as named above

\copyrightpage{~Seyed Yahya Shirazi}
% includes copyright symbol. Term year is automatically inserted before the author name.  Replace the author name with your own, but keep the tilde in place. 

\begin{abstract}
Seated locomotor tasks such as cycling or recumbent stepping improve walking performance during rehabilitation. Cortical control during walking is most pronounced when the person is perturbed. But, the electrocortical dynamics during perturbed seated tasks has not been studied in detail. The primary purpose of this research was to quantify cortical and muscular responses to mechanical perturbations during recumbent stepping. We also aimed to quantify possible differences between young and older adults' responses to perturbed stepping. Before 
% abstract files can be added here.  I recommend using \input over \include
\end{abstract}

\dedication{Dedicated to my love, Maryam.}
% creates vertically and horizontally centered dedication page.  If larger than a paragraph, remove the \vspace*fil commands from the dedication section in the class file.

\begin{acknowledgments}
The acknowledgments page is optional. If you choose to use it, it should appear after the Abstract, but before the Table of Contents.
\end{acknowledgments}

\tableofcontents

\listoffigures

\listoftables

\mainmatter
% restarts page numbering with arabic numbers

\subfileinclude{chapters/chap0}

\subfileinclude{chapters/chap1}

\subfileinclude{chapters/chap2}

\subfileinclude{chapters/chap3}

\appendix

\chapter{TITLE OF APPENDIX}
\newpage
% You must include a \newpage command after each appendix.  And each appendix can be inserted as a chapter after the \appendix command.  

% This template is set to auto-letter multiple appendices.  

% If you change the secnumdepth to -1  and use multiple appendices, you must include the appendix name with the appendix title, such as APPENDIX A: TITLE.  If you have only one appendix, title it APPENDIX: TITLE.

% If you use chapter numbering and have only one appendix, you will need to comment out line 753 in the class file, containing the command \gdef\thechapter{\@Alph\c@chapter}}, and uncomment line 754 to define \gdef\thechapter{}} and remove the auto-lettering.


\noindent\labelitemi{~Begin appendix text on the page following the buffer page by using the newpage command.}\\
\labelitemi{~Continue Arabic pagination; do not restart page numbering with an appendix}\\
\labelitemi{~Use the same style and format for buffer page headings as you do for other body chapter headings.}\\
\labelitemi{~Letter, don't number, appendixes (e.g. APPENDIX A, APPENDIX B, etc.)}\\
\labelitemi{~If you have only one appendix, do not letter it at all}\\
\labelitemi{~Appendixes should follow the margin and other formatting requirements from the rest of the document}\\


\chapter{SECOND APPENDIX}
\newpage

Supplementary documentation.

\backmatter

% \begin{thebibliography}{99}

% \bibitem{Turkle95}
% 	Sherry Turkle,
% 	\emph{Life on the Screen}.
% 	Cambridge, MA: MIT Press,
% 	1995.

% % this template does not include any packages for references.  It is compatible with natbib and other common reference packages, but you will need to add them to the document.
% \end{thebibliography}

\end{document}